
title: "R Notebook"
output: html_notebook


#Importing the required datasets for analysis
fifa_data=readr::read_csv("C:\\Users\\krishna\\Desktop\\PROJECT\\2020SEPT\\fifa_project.csv")


bundesliga <- c(
  "SC Paderborn 07", "1. FSV Mainz 05", "Bayer 04 Leverkusen", "FC Bayern Munchen",
  "Borussia Dortmund", "Borussia Monchengladbach", "Eintracht Frankfurt",
  "FC Augsburg", "FC Schalke 04", "Fortuna Dusseldorf", "1. FC Union Berlin",
  "Hertha BSC", "RB Leipzig", "SC Freiburg", "TSG 1899 Hoffenheim",
  "1. FC Koln", "VfL Wolfsburg", "SV Werder Bremen"
)

premierLeague <- c(
  "Arsenal", "Bournemouth", "Brighton & Hove Albion", "Burnley",
  "Norwich City", "Chelsea", "Crystal Palace", "Everton", "Sheffield United",
  "Aston Villa", "Leicester City", "Liverpool", "Manchester City",
  "Manchester United", "Newcastle United", "Southampton", 
  "Tottenham Hotspur", "Watford", "West Ham United", "Wolverhampton Wanderers")
  
laliga <- c(
  "Athletic Club de Bilbao", "Atletico Madrid", "CD Leganes",
  "Deportivo Alaves", "FC Barcelona", "Getafe CF", 
  "Levante UD", "RC Celta", "RCD Espanyol", 
  "Real Betis", "Real Madrid", "Real Sociedad", "Real Valladolid CF",
  "SD Eibar", "Sevilla FC", "Valencia CF", "Villarreal CF",
  "CA Osasuna","Granada CF","RCD Mallorca"
)



seriea <- c(
  "Atalanta","Bologna","Cagliari", "Fiorentina","Genoa",
  "Inter","Juventus","Lazio","Milan","Napoli","Parma","Roma","Sampdoria","Sassuolo","SPAL",
  "Torino","Udinese","Brescia","Lecce","Hellas Verona")



ligue1 <- c(
  "Amiens SC", "Angers SCO", "AS Monaco", "AS Saint-etienne", "Dijon FCO", "FC Metz",
  "FC Nantes", "FC Girondins de Bordeaux", "LOSC Lille", "Montpellier HSC", "Nimes Olympique", 
  "OGC Nice", "Olympique Lyonnais","Olympique de Marseille", "Paris Saint-Germain", 
  "RC Strasbourg Alsace", "Stade Brestois 29", "Stade de Reims", "Stade Rennais FC", "Toulouse Football Club")
  
  
  
  
  

  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
```{r}

library(dplyr)
#Creating league for teams

temp=fifa_data %<>% mutate(League = if_else(club %in% bundesliga, "Bundesliga",
                                  if_else(club %in% premierLeague, "Premier League", 
                                          if_else(club %in% laliga, "La Liga", 
                                                  if_else(club %in% seriea, "Serie A", 
                                                                  if_else(club %in% ligue1, "Ligue 1",NA_character_))))),
                 
                 Country = if_else(League == "Bundesliga", "Germany",
                                   if_else(League == "Premier League", "UK",
                                           if_else(League == "La Liga", "Spain", 
                                                   if_else(League == "Serie A", "Italy", 
                                                           if_else(League == "Ligue 1", "France", NA_character_)))))) %>% 
  filter(!is.na(League)) %>% mutate_if(is.factor, as.character())


rm(bundesliga, premierLeague, laliga, seriea, ligue1)

```

```{r}
# 5. Position Class -------------------------------------------------------
library(dplyr)
library(magrittr)
# Create Position Class #
defence <- c("CB", "RB", "LB", "LWB", "RWB", "LCB", "RCB")
midfielder <- c("CM", "CDM","CAM","LM","RM", "LAM", "RAM", "LCM", "RCM", "LDM", "RDM")

temp %<>% mutate(Class = if_else(player_positions %in% "GK", "Goal Keeper",
                                 if_else(player_positions %in% defence, "Defender",
                                         if_else(player_positions %in% midfielder, "Midfielder", "Forward"))))

rm(defence, midfielder)
```



# To change values to characters
```{r}
#Formatting nos to currncy
val<- function(x) {
  dplyr::case_when(
      x < 1e3 ~ as.character(x),
      x < 1e6 ~ paste0(as.character(x/1e3), "K"),
      x < 1e9 ~ paste0(as.character(x/1e6), "M"),
      TRUE ~ "To be implemented..."
  )
}
test=val(temp$value_eur)
```

```{r}
val1<- function(y) {
  dplyr::case_when(
      y < 1e3 ~ as.character(y),
      y < 1e6 ~ paste0(as.character(y/1e3), "K"),
      y < 1e9 ~ paste0(as.character(y/1e6), "M"),
      TRUE ~ "To be implemented..."
  )
}
test1=val1(temp$wage_eur)

```

```{r}
temp1=temp  %>% 
  mutate(
    Value=val(temp$value_eur),
    Wages=val1(temp$wage_eur)
  )
```


```{r}
temp1$value_eur = paste0('€', temp1$Value)
temp1$wage_eur=paste0('€',temp1$Wages)
```


```{r eval=FALSE, include=FALSE}
#library(gt)
#choosing currencries as euros
#temp %>% 
  dplyr::select(value_eur,wage_eur) %>%
 # gt() %>%
  fmt_currency(
    columns = vars(value_eur),
    currency = "EUR"
  ) %>%
  fmt_currency(
    columns = vars(wage_eur),
    currency = "EUR"
  )
```


```{r}
temp1 <- temp1 %>% arrange(Player) %>% mutate(Name.Pos = paste0(as.character(Player),", ", as.character(player_positions))) 
```



```{r}
write.csv(temp1,"C:\\Users\\krishna\\Desktop\\PROJECT\\2020SEPT\\ori_FIFA.csv")
```










```{r}
df=read.csv("C:\\Users\\krishna\\Desktop\\PROJECT\\2020SEPT\\FIFA.csv")
View(df)
```


```{r}
library(plotly)

fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  ) 
fig <- temp1 %>%
  add_trace(
    r = c(),
    theta = c('A','B','C', 'D', 'E', 'A'),
    name = temp$Player
  ) 
fig <- fig %>%
  add_trace(
    r = c(1.5, 10, 39, 31, 15, 1.5),
    theta = c('A','B','C', 'D', 'E', 'A'),
    name = temp$Player
  ) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,100)
      )
    )
  )

fig
```
/

```{r}

fig <- plot_ly(
    type = 'scatterpolar',
    r = c( 88,96),
    theta = c(temp$overall,temp$potential),
    fill = 'toself'
  ) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,100)
      )
    ),
    showlegend = F
  )

fig
```


#Pre-processing of fbref data set for 2019/20 top 5 european leagues

```{r}
setwd("C:\\Users\\krishna\\Desktop\\FactorAnalysis-master\\FactorAnalysis-master")
```



```{r}
BigFiveStandard <- read.csv('OverallStats.txt')
```















library(dplyr)

# Import data from 19/20 season from fbref

#Overall stats
BigFiveoverall<- read.csv("C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\OverallStats.txt")

BigFiveoverall<-select(BigFiveoverall,"Player","Squad","Pos","Gls","Ast",
                         "Comp","Min","Glsp90","Astp90",
                         "npxGp90","xAp90","Age")


#Creation stats
BigFiveCreate <- read.csv("C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\Creation.txt")


BigFiveCreate <-select(BigFiveCreate,"Player","Squad","SCA90",
                         "ShotPassLive","ShotPassDead","ShotDrib",
                         "ShotSh","ShotFoul","GCA90","GoalPassLive",
                         "GoalPassDead","GoalDrib","GoalSh",
                         "GoalFoul")

#Defence stats
BigFiveDef <- read.csv('C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\Defence.txt')

BigFiveDef <-select(BigFiveDef,"Player","Squad",
                        "Tklp90",
                        "Pressp90","SuccPressp90","Def3rdPresp90",
                        "Mid3rdPresp90","Att3rdPresp90",
                        "Def3rdTklp90","Mid3rdTklp90",
                         "Att3rdTklp90","Tkl.","DribbledPastp90",
                         "SuccPressp90","Def3rdPresp90","Mid3rdPresp90",
                         "Att3rdPresp90","Intp90","Clrp90",
                         "Errp90")

#Misc Stats
BigFiveMiscs <- read.csv('C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\Misc.txt')

BigFiveMiscs <-select(BigFiveMiscs,"Player","Squad",
                        "FlsCommittedp90","FlsDrawnp90",
                        "Offp90","Crsp90","RecovBalls",
                        "WonAerialp90","LostAerialp90")


#Passing Stats
BigFivePass <- read.csv('C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\Passing.txt')

BigFivePass <- select(BigFivePass,"Player","Squad",
                     "PassTotDistp90","PassPrgDistp90",
                     "CmpShortp90","AttShortp90","CmpMediump90",
                     "AttMediump90","CmpTotalp90","AttTotalp90",
                     "CmpLongp90","AttLongp90","KPp90","PassIntoFinalThirdp90",
                     "PPAp90","ProgPassp90")

#Passing Stats
BigFivePoss <- read.csv('C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\Possession.txt')

BigFivePoss <-select(BigFivePoss,"Player","Squad",
                       "Touchesp90","DefPenTouchesp90",
                       "Def3rdTouchesp90","Mid3rdTouchesp90","Att3rdTouchesp90",
                       "AttPenTouchesp90","LiveTouches","SuccDribblesp90","AttDribblesp90",
                       "Carriesp90","TotDistCarriedp90","PrgDistCarriedp90",
                       "RecPassp90","Dispossessedp90")

#Shots Stats
BigFiveShot <- read.csv('C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\Shooting.txt')

BigFiveShot <-select(BigFiveShot,"Player","Squad",
                           "Sh.90","SoT.90")

#Pass Type Stats
BigFivePassTyp <- read.csv('C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\FactorAnalysis-master\\PassTypes.txt')

BigFivePassTyp <-select(BigFivePassTyp,"Player","Squad",
                      "ThroughBallp90","PassUnderPress",
                      "Switches","GroundPasses","LowPasses",
                      "HighPasses","PassesInt")


#Join DFs
alldata_fbref<-merge(x = BigFiveoverall, y = BigFiveCreate, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

alldata_fbref<-merge(x = alldata_fbref, y = BigFiveDef, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

alldata_fbref<-merge(x = alldata_fbref, y = BigFiveMiscs, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

alldata_fbref<-merge(x = alldata_fbref, y = BigFivePass, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

alldata_fbref<-merge(x = alldata_fbref, y = BigFivePoss, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

alldata_fbref<-merge(x = alldata_fbref, y = BigFiveShot, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

alldata_fbref<-merge(x = alldata_fbref, y = BigFivePassTyp, by = c("Player","Squad"), all.x = TRUE)
alldata_fbref<-alldata_fbref[complete.cases(alldata_fbref),]

#Create clean version of player name
alldata_fbref['Name']<-sub("\\\\.*", "", alldata_fbref$Player)

#Convert recovered balls to per 90
alldata_fbref$RecovBallsp90<-alldata_fbref$RecovBalls/(alldata_fbref$Min/90)

#writing into a csv file

write.csv(alldata_fbref,"C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\data\\fbref_201920.csv")
#Filter on players >=500 mins played
Overall1920<-filter(Overall1920,Min>=500)

#Import data from squads to scale some statistics

#Squad possession and touches data
Possession <- read.csv('SquadsTouches.txt')
Possession <- select(Possession,"Squad","Comp","Poss","Touches")

#Squad attempted passes data
Passes <- read.csv('SquadsPasses.txt')
Passes <- select(Passes,"Squad","Comp","AttSquad")

#Squad minutes played data
Mins <- read.csv('SquadsMins.txt')
Mins <- select(Mins,"Squad","Comp","SquadMin")

#Merge squad data into player data
Overall1920<-merge(x = Overall1920, y = Possession, by = c("Squad","Comp"), all.x = TRUE)
Overall1920<-Overall1920[complete.cases(Overall1920),]

Overall1920<-merge(x = Overall1920, y = Passes, by = c("Squad","Comp"), all.x = TRUE)
Overall1920<-Overall1920[complete.cases(Overall1920),]

Overall1920<-merge(x = Overall1920, y = Mins, by = c("Squad","Comp"), all.x = TRUE)
Overall1920<-Overall1920[complete.cases(Overall1920),]














#NEW DATA TO PRE-PROCESS

```{r}
new_dat=read.csv("C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\data\\fbref_201920.csv")
```

```{r}
utils::View(new_dat)
```



```{r}
library(dplyr)
fwds=new_dat %>%filter(Pos=='FW')
```

```{r}
utils::View(fwds)
```


```{r}
mids=new_dat %>% filter(Pos=='MF')
```

```{r}
utils::View(mids)
```

```{r}
dfs=new_dat %>% filter(Pos=='DF')

```

```{r}
utils::View(dfs)
```




```{r}
write.csv(fwds,"C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\data\\2019fwds.csv")
write.csv(mids,"C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\data\\2019mids.csv")
write.csv(dfs,"C:\\Users\\krishna\\Desktop\\PROJECT-2020\\FactorAnalysis-master\\data\\2019defs.csv")
```

